Structured Versus Decorated Cospans

### 2021-06-20 cospans_new.tex
Completed proof of Thm. 2.5, but see stuff in red.
Working on the proof of Thm. 3.1

% Structured versus decorated cospans
% John Baez, Kenny Courser and Christina Vasilakopoulou
% in LaTeX
% 2021/6/8 - Finishing up

@@

Next, one can check that $\Phi$ is a fibration.  Given a morphism $f \maps a \to a'$ in $\A$ and an object $(a' \xrightarrow{i'} b', x') \in \A/U$ over $a'$, a cartesian lifting of $f$ is given by 
\[ (f,1,1) \maps (a \xrightarrow{i' f} b' , x')\; \to \; (a' \xrightarrow{i'} b', x'). \]
Denoting this cartesian lifting by $\textnormal{cart}(f)$, the tensor product of $\A/U$ strictly preserves such cartesian liftings in the sense that $\textnormal{cart}(f_1) \otimes \textnormal{cart}(f_2)=\textnormal{cart}(f_1+f_2)$.

@@

It follows that $\Phi$ is a bifibration.  Denoting the cocartesian lifting of a morphism $f$ by $\textnormal{cocart}(f)$, we have that $\textnormal{cocart}(f_1) \otimes \textnormal{cocart}(f_2) \cong \textnormal{cocart}(f_1+f_2)$ by the universal map between two colimits of the same diagram.  Thus, $\Phi$ is a monoidal bifibration.

Lastly, we need to check that $\Phi$ satisfies the Beck--Chevalley condition.  Merely from the fact that $\Phi$ is a bifibration, for any commutative square in $\A$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1.5,0) {$b$};
\node (C) at (0,-1) {$c$};
\node (D) at (1.5,-1) {$d$};
\label{bc-square}
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$h$} (B)
(A) edge node[left]{$k$} (C)
(B) edge node[right]{$g$} (D)
(C) edge node[below]{$f$} (D);
\end{tikzpicture}
\]
there is a natural transformation
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$(\A/U)_a$};
\node (B) at (1.5,0) {$(\A/U)_b$};
\node (C) at (0,-1) {$(\A/U)_c$};
\node (D) at (1.5,-1) {$(\A/U)_d$.};
\node (E) at (0.75,-0.5) {$\Searrow \theta$};
\path[->,font=\scriptsize,>=angle 90]
(B) edge node[above]{$h^*$} (A)
(A) edge node[left]{$k_!$} (C)
(B) edge node[right]{$g_!$} (D)
(D) edge node[below]{$f^*$} (C);
\end{tikzpicture}
\]
as defined at the end of \cref{subsec:fibrations}.   We need to prove that when the square in $\A$ is 
a pushout, $\theta$ is a natural isomorphism.

@@

\begin{thm}
\label{thm:functoriality}
Given categories $\A$ and $\A'$ with finite colimits, lax monoidal pseudofunctors $F, F' \maps (\A',+) \to (\Cat,\times)$, a finite colimit preserving functor $H \maps \A \to \A'$, a lax monoidal pseudofunctor $E \maps (\Cat,\times) \to (\Cat,\times)$ and a {\john monoidal???} natural isomorphism $\theta$ as in the following diagram:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$\A$};
\node (B) at (1,0) {$\Cat$};
\node (C) at (0,-1) {$\A'$};
\node (D) at (1,-1) {$\Cat$};
\node (E) at (0.5,-0.5) {$\Swarrow \theta$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$F$} (B)
(A) edge node[left]{$H$} (C)
(B) edge node[right]{$E$} (D)
(C) edge node[below]{$F'$} (D);
\end{tikzpicture}
\] 
we obtain a double functor $\lH \maps F\lCsp \to F'\lCsp$ defined as above.  If $F, F'$ and $E$ are symmetric, then $\|H \maps F\lCsp \to F'\lCsp$ is a symmetric monoidal double functor. 
\end{thm}

@@

In \cite{BC}, the first two authors introduced structured cospans as a formalism to describe open networks.   Here we recall this and give a new construction of the double category of structured
cospans that, in the next section, we use to clarify their relation to decorated cospans.

\begin{thm}\label{thm:SC}
Given categories $\A$ and $\X$ with finite colimits and $L \maps \A \to \X$ a functor preserving finite colimits, there is a symmetric monoidal double category $_L\lCsp(\X)$ in which
\begin{itemize}
\item an object is an object of $\A$,
\item a vertical 1-morphism is a morphism of $\A$,
\item a horizontal 1-cell from $a$ to $b$ is an $L$-\define{structured cospan}, that is,
a diagram in $\X$ of the form
\begin{displaymath}
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(a)$};
\node (B) at (1,0) {$x$};
\node (C) at (2,0) {$L(b)$,};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\end{displaymath}
\item a 2-morphism is a \define{map of} $L$-\define{structured cospans}, that is, a commutative diagram in $\X$ of the form
\begin{displaymath}
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(a)$};
\node (B) at (1,0) {$x$};
\node (C) at (2,0) {$L(b)$};
\node (A') at (0,-1) {$L(a')$};
\node (B') at (1,-1) {$x'$};
\node (C') at (2,-1) {$L(b')$.};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A') edge node[below]{$i'$} (B')
(C') edge node[below]{$o'$} (B')
(A) edge node [left]{$L(f)$} (A')
(B) edge node [left]{$\alpha$} (B')
(C) edge node [right]{$L(g)$} (C');
\end{tikzpicture}
\end{displaymath}
\end{itemize}
Composition of horizontal 1-cells and 2-cells is done using pushouts in $\X$, and the
symmetric monoidal structure is defined using finite coproducts in $\A$ and $\X$: 
the tensor product of two horizontal 1-cells is
\begin{equation}\label{eq:tensorstuctured}
\begin{tikzcd}[column sep={.4in,between origins}, row sep=.08in]
& x &&&& x' &&&& x+x' & \\
&&&\ot&&&& = &&&& \\
L(a)\ar[uur,"i" pos=0.3]&& L(b)\ar[uul,"o"' pos=0.3] && L(a')\ar[uur,"i'" pos=0.3] && L(b')\ar[uul,"o'"' pos=0.3] && L(a+a')\ar[uur,"i+i'" pos=0.3] && L(b+b')\ar[uul,"o+o'"' pos=0.3] 
\end{tikzcd}
\end{equation}
using that $L$ preserves finite coproducts.
\end{thm}

@@

{\bf NEW PROOF HERE.}  We apply \cref{lem:shulman} to $L/X \to A$.   Why is this a fibration, cofibration, Beck--Chevalley and symmetric monoidal?

The proof is analogous to the proof of \cref{thm:decorated_cospans_1} in that we apply \cref{lem:shulman} to the Beck-Chevalley symmetric monoidal bifibration $\Psi \maps (L/\X) \to \A$ which we now define. Let $(L/\X)$ be the comma category in which:
\begin{enumerate}
\item{an object is a triple $(a,x,L(a) \xrightarrow{I} x)$, and}
\item{a morphism from $(a,x,L(a) \xrightarrow{I} x)$ to $(a',x',L(a') \xrightarrow{I'} x')$ is a pair of morphisms $f \maps a \to a'$ and $\alpha \maps x \to x'$ such that the following square commutes:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(a)$};
\node (B) at (1,0) {$L(a')$};
\node (C) at (0,-1) {$x$};
\node (D) at (1,-1) {$x'$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$L(f)$} (B)
(A) edge node[left]{$I$} (C)
(B) edge node[right]{$I'$} (D)
(C) edge node[above]{$\alpha$} (D);
\end{tikzpicture}
\]}
\end{enumerate}
The functor $\Psi$ is defined on objects by $\Psi(a,x,L(a) \xrightarrow{I} x)=a$ and on morphisms by $\Psi(f,\alpha)=f$. The monoidal structure of $(L/\X)$ is similar to the monoidal structure of $(\A/U)$ of \cref{thm:decorated_cospans_1} in that the tensor product of two objects $(a_1,x_1,L(a_1) \xrightarrow{I_1} x_1)$ and $(a_2,x_2,L(a_2) \xrightarrow{I_2} x_2)$ is given by 
$$(a_1,x_1,L(a_1) \xrightarrow{I_1} x_1) \otimes (a_2,x_2,L(a_2) \xrightarrow{I_1} x_2)=(a_1+a_2,x_1+x_2,L(a_1+a_2) \xrightarrow{I_1+I_2} x_1+x_2)$$
where again the natural isomorphism $L(a_1)+L(a_2) \cong L(a_1+a_2)$ is implicit. The monoidal unit is ${(0_\A,0_\X,{L(0_\A) \to 0_\X})}$, and it is clear that $\Psi$ is a strict monoidal functor using this tensor product.

The functor $\Psi$ is both a fibration and an opfibration. Given a morphism $f \maps a \to b$ in $\A$ with ${(b,x,L(b) \xrightarrow{I} x)}$ in $\X$ over $b$, the cartesian lifting of $f$ is given by
$$(f,\id_x) \maps (a,x,L(a) \xrightarrow{I \circ L(f)} x) \to (b,x,L(b) \xrightarrow{I} x).$$
With $(a,x,L(a) \xrightarrow{I} x)$ in $\X$ over $a$, the cocartesian lifting of $f$ is given by
$$(f,\kappa) \maps (a,x,L(a) \xrightarrow{I} x) \to (b,x+_{L(a)} L(b),L(b) \xrightarrow{\theta} x+_{L(a)} L(b))$$
where $\kappa$ and $\theta$ are as in the following diagram:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(a)$};
\node (B) at (2.25,0) {$L(c)$};
\node (C) at (1.5,1) {$L(b)$};
\node (D) at (0,-2) {$x$};
\node (E) at (2.25,-2) {$y$};
\node (F) at (1.5,-1) {$x+_{L(a)} L(b)$};
\path[->,font=\scriptsize,>=angle 90]
(D) edge [dashed] node [above] {$\kappa$} (F)
(F) edge [dashed] node [left] {$\exists ! \psi$} (E)
(D) edge node [above] {$g'$} (E)
(A) edge node [left] {$I$} (D)
(C) edge [dashed] node [left,near end] {$\theta$} (F)
(B) edge node {$$} (E)
(A) edge node[above]{$L(f')$} (B)
(C) edge node [right] {$L(p)$} (B)
(A) edge node[left]{$L(f)$} (C);
\end{tikzpicture}
\]
Both cartesian and cocartesian liftings are preserved by the tensor product of $(L/\X)$.

Lastly, we show that $\Psi \maps (L/ \X) \to \A$ satisfies the Beck-Chevalley condition. Given a pushout square in $\A$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$b$};
\node (C) at (0,-1) {$c$};
\node (D) at (1,-1) {$d$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$h$} (B)
(A) edge node[left]{$k$} (C)
(B) edge node[right]{$g$} (D)
(C) edge node[above]{$f$} (D);
\end{tikzpicture}
\]
we show that the following square commutes up to a natural isomorphism:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$(L/\X)_a$};
\node (B) at (2,0) {$(L/\X)_b$};
\node (C) at (0,-1) {$(L/\X)_c$};
\node (D) at (2,-1) {$(L/\X)_d$};
\node (E) at (1,-0.5) {$\cong$};
\path[->,font=\scriptsize,>=angle 90]
(B) edge node[above]{$h^*$} (A)
(A) edge node[left]{$k_!$} (C)
(B) edge node[right]{$g_!$} (D)
(D) edge node[above]{$f^*$} (C);
\end{tikzpicture}
\]
Let $(b,x,L(b) \xrightarrow{I} x)$ be an object of $(L/\X)_b$. Going right, we precompose with $L(h) \maps L(a) \to L(b)$ to obtain the object $(a,x,L(a) \xrightarrow{I \circ L(h)} x)$ in $(L/\X)_a$. Then, going down, we pushforward along $L(k) \maps L(a) \to L(c)$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(a)$};
\node (B) at (2,0) {$x$};
\node (C) at (0,-1) {$L(c)$};
\node (D) at (2,-1) {$L(c)+_{L(a)}x$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$I \circ L(h)$} (B)
(A) edge node[left]{$L(k)$} (C)
(B) edge node[right]{$$} (D)
(C) edge node[above]{$\psi$} (D);
\end{tikzpicture}
\]
to obtain the object $(c,L(c)+_{L(a)} x,L(c) \xrightarrow{\psi} L(c)+_{L(a)} x)$ in $(L/ \X)_c$. For the other route, first going down, we pushforward the object $(b,x,L(b) \xrightarrow{I} x)$ along $L(g) \maps L(b) \to L(d)$ by taking the following pushout:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(b)$};
\node (B) at (2,0) {$x$};
\node (C) at (0,-1) {$L(d)$};
\node (D) at (2,-1) {$L(d)+_{L(b)}x$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$I$} (B)
(A) edge node[left]{$L(g)$} (C)
(B) edge node[right]{$$} (D)
(C) edge node[above]{$\theta$} (D);
\end{tikzpicture}
\]
which yields the object $(d,L(d)+_{L(b)}x,L(d) \xrightarrow{\theta} L(d)+_{L(b)} x)$ of $(L/\X)_d$. We then precompose with $L(f) \maps L(c) \to L(d)$ to obtain the object $(c,L(d)+_{L(b)} x,L(c) \xrightarrow{\theta \circ L(f)} L(d)+_{L(b)} x)$ of $(L/\X)_c$.

>>>>

% Structured versus decorated cospans
% John Baez, Kenny Courser and Christina Vasilakopoulou
% in LaTeX
% 2021/6/20 - Finishing up

@@

Next, one can check that $\Phi$ is a fibration.  Given a morphism $f \maps a \to a'$ in $\A$ and an object $(a' \xrightarrow{i'} b', x') \in \A/U$ over $a'$, a cartesian lifting of $f$ to this object is given by 
\[ (f,1,1) \maps (a \xrightarrow{i' f} b' , x')\; \to \; (a' \xrightarrow{i'} b', x'). \]
Denoting the cartesian lifting of $f$ to the object $z \in \A/U$ by $\mathrm{Cart}(f,z)$, the tensor product of $\A/U$ strictly preserves such cartesian liftings in the sense that $\mathrm{Cart}(f_1,z_1) \otimes \mathrm{Cart}(f_2,z_2)=\mathrm{Cart}(f_1 \otimes f_2, z_1 \otimes z_2)$.

@@

It follows that $\Phi$ is a bifibration.  Denoting the cocartesian lifting of a morphism $f$ to an object $z \in \A/U$ by $\mathrm{Cocart}(f,z)$, we have that $\mathrm{Cocart}(f_1,z_1) \otimes \mathrm{Cocart}(f_2,z_2) \cong \mathrm{Cocart}(f_1 \otimes f_2,z_1 \otimes z_2)$ by the universal map between two colimits of the same diagram.    Thus, $\Phi$ is a monoidal bifibration.

Lastly, we need to check that $\Phi$ satisfies the Beck--Chevalley condition.  Merely from the fact that $\Phi$ is a bifibration, for any commutative square in $\A$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1.5,0) {$b$};
\node (C) at (0,-1) {$c$};
\node (D) at (1.5,-1) {$d$};
\label{bc-square}
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$h$} (B)
(A) edge node[left]{$k$} (C)
(B) edge node[right]{$g$} (D)
(C) edge node[below]{$f$} (D);
\end{tikzpicture}
\]
there is a natural transformation
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$(\A/U)_a$};
\node (B) at (1.5,0) {$(\A/U)_b$};
\node (C) at (0,-1) {$(\A/U)_c$};
\node (D) at (1.5,-1) {$(\A/U)_d$.};
\node (E) at (0.75,-0.5) {$\Searrow \theta$};
\path[->,font=\scriptsize,>=angle 90]
(B) edge node[above]{$h^*$} (A)
(A) edge node[left]{$k_!$} (C)
(B) edge node[right]{$g_!$} (D)
(D) edge node[below]{$f^*$} (C);
\end{tikzpicture}
\]
defined in Equation \eqref{theta}.   We need to prove that when the square in $\A$ is 
a pushout, $\theta$ is a natural isomorphism.

@@

\begin{thm}
\label{thm:functoriality}
Given categories $\A$ and $\A'$ with finite colimits, lax monoidal pseudofunctors $F, F' \maps (\A',+) \to (\Cat,\times)$, a finite colimit preserving functor $H \maps \A \to \A'$, a lax monoidal pseudofunctor $E \maps (\Cat,\times) \to (\Cat,\times)$ and a natural isomorphism $\theta$ as in the following diagram:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$\A$};
\node (B) at (1,0) {$\Cat$};
\node (C) at (0,-1) {$\A'$};
\node (D) at (1,-1) {$\Cat$};
\node (E) at (0.5,-0.5) {$\Swarrow \theta$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$F$} (B)
(A) edge node[left]{$H$} (C)
(B) edge node[right]{$E$} (D)
(C) edge node[below]{$F'$} (D);
\end{tikzpicture}
\] 
we obtain a double functor $\lH \maps F\lCsp \to F'\lCsp$ defined as above.  If $F, F'$ and $E$ are symmetric, then $\|H \maps F\lCsp \to F'\lCsp$ is a symmetric monoidal double functor. 
\end{thm}

@@

Structured cospans are an alternative approach to equipping the apex of a cospan with 
extra data \cite{BC}.    Here we recall this formalism and give a new construction of the double category of structured cospans that clarifies their relation to decorated cospans.  This new construction again uses Shulman's \cref{lem:shulman}.

\begin{thm}\label{thm:SC}
Given categories $\A$ and $\X$ with finite colimits and $L \maps \A \to \X$ a functor preserving finite colimits, there is a symmetric monoidal double category $_L\lCsp(\X)$ in which
\begin{itemize}
\item an object is an object of $\A$,
\item a vertical 1-morphism is a morphism of $\A$,
\item a horizontal 1-cell from $a$ to $b$ is an $L$-\define{structured cospan}, that is,
a diagram in $\X$ of the form
\begin{displaymath}
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(a)$};
\node (B) at (1,0) {$x$};
\node (C) at (2,0) {$L(b)$,};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\end{displaymath}
\item a 2-morphism is a \define{map of} $L$-\define{structured cospans}, that is, a commutative diagram in $\X$ of the form
\begin{displaymath}
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(a)$};
\node (B) at (1,0) {$x$};
\node (C) at (2,0) {$L(b)$};
\node (A') at (0,-1) {$L(a')$};
\node (B') at (1,-1) {$x'$};
\node (C') at (2,-1) {$L(b')$.};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A') edge node[below]{$i'$} (B')
(C') edge node[below]{$o'$} (B')
(A) edge node [left]{$L(f)$} (A')
(B) edge node [left]{$\alpha$} (B')
(C) edge node [right]{$L(g)$} (C');
\end{tikzpicture}
\end{displaymath}
\end{itemize}
Vertical composition is done using composition in $\A$, while horizontal composition 
is done using pushouts in $\X$. The tensor product of two horizontal 1-cells is
\[
\begin{tikzcd}[column sep={.4in,between origins}, row sep=.08in]
& x &&&& x' &&&& x+x' & \\
&&&\ot&&&& = &&&& \\
L(a)\ar[uur,"i" pos=0.3]&& L(b)\ar[uul,"o"' pos=0.3] && L(a')\ar[uur,"i'" pos=0.3] && L(b')\ar[uul,"o'"' pos=0.3] && L(a+a')\ar[uur,"i+i'" pos=0.3] && L(b+b')\ar[uul,"o+o'"' pos=0.3] 
\end{tikzcd}
\]
where $i + i'$ and $o + o'$ are defined using the fact that $L$ preserves binary coproducts, and tensor product of two 2-morphisms is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (E) at (3,0) {$L(a_1)$};
\node (F) at (5,0) {$L(b_1)$};
\node (G) at (4,0) {$x_1$};
\node (E') at (3,-1) {$L(a_2)$};
\node (F') at (5,-1) {$L(b_2)$};
\node (G') at (4,-1) {$x_2$};
\node (E'') at (6.5,0) {$L(a_1')$};
\node (F'') at (8.5,0) {$L(b_1')$};
\node (G'') at (7.5,0) {$x_1'$};
\node (E''') at (6.5,-1) {$L(a_2')$};
\node (F''') at (8.5,-1) {$L(b_2')$};
\node (G''') at (7.5,-1) {$x_2'$};
\node (X) at (5.75,-0.5) {$\otimes$};
\node (E'''') at (4,-2) {$L(a_1 + a_1')$};
\node (F'''') at (7.5,-2) {$L(b_1 + b_1')$};
\node (G'''') at (5.75,-2) {$x_1 + x_1'$};
\node (E''''') at (4,-3) {$L(a_2 + a_2')$};
\node (F''''') at (7.5,-3) {$L(b_2 + b_2').$};
\node (G''''') at (5.75,-3) {$x_2 + x_2'$};
\node (Y) at (3,-2.5) {$=$};
\path[->,font=\scriptsize,>=angle 90]
(F) edge node[above]{$o_1$} (G)
(E) edge node[left]{$L(f)$} (E')
(F) edge node[right]{$L(g)$} (F')
(G) edge node[left]{$\alpha$} (G')
(E) edge node[above]{$i_1$} (G)
(E') edge node[below]{$i_2$} (G')
(F') edge node[below]{$o_2$} (G')
(F'') edge node[above]{$o_1'$} (G'')
(E'') edge node[left]{$L(f')$} (E''')
(F'') edge node[right]{$L(g')$} (F''')
(G'') edge node[left]{$\alpha'$} (G''')
(E'') edge node[above]{$i_1'$} (G'')
(E''') edge node[below]{$i_2'$} (G''')
(F''') edge node[below]{$o_2'$} (G''')
(F'''') edge node[above]{$o_1 + o_1'$} (G'''')
(E'''') edge node[left]{$L(f + f')$} (E''''')
(F'''') edge node[right]{$L(g + g')$} (F''''')
(G'''') edge node[left]{$\alpha + \alpha'$} (G''''')
(E'''') edge node[above]{$i_1 + i_1'$} (G'''')
(E''''') edge node[below]{$i_2 + i_2'$} (G''''')
(F''''') edge node[below]{$o_2 + o_2'$} (G''''');
\end{tikzpicture}
\]
\end{thm}

@@

Our new proof is analogous to that of \cref{thm:decorated_cospans_1} in that we apply \cref{lem:shulman} to a Beck--Chevalley symmetric monoidal bifibration $\Psi \maps L/\X \to \A$,
and define ${}_L \lCsp(\X)$ to be $\Fr(\Psi)$.    First, note that in the comma category $L/\X$:
\begin{itemize}
\item an object is a pair $(a, L(a) \xrightarrow{} x)$ consisting of an object $a \in \A$ and a morphism $L(a) \xrightarrow{i} x$ in $\X$;
\item a morphism from $(a,L(a) \xrightarrow{i} x)$ to $(a',L(a') \xrightarrow{i'} x')$ is a pair $(f,g)$ of morphisms $f \maps a \to a'$ and $g \maps x \to x'$ such that this square commutes:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(a)$};
\node (B) at (1.5,0) {$L(a')$};
\node (C) at (0,-1) {$x$};
\node (D) at (1.5,-1) {$x'$.};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$L(f)$} (B)
(A) edge node[left]{$i$} (C)
(B) edge node[right]{$i'$} (D)
(C) edge node[below]{$g$} (D);
\end{tikzpicture}
\]
\end{itemize}
Next, we define the functor $\Psi \maps L/\X \to \A$ on objects by $\Psi(a,L(a) \xrightarrow{i} x)=a$ and on morphisms by $\Psi(f,g)=f$.

The monoidal structure of $L/\X$ is similar to the monoidal structure of $\A/U$ of \cref{thm:decorated_cospans_1} in that the tensor product of two objects $(a,L(a) \xrightarrow{i} x)$ and $(a,L(a) \xrightarrow{i'} x')$ is given by 
\[  (a,L(a) \xrightarrow{i} x) \otimes (a',L(a') \xrightarrow{i'} x')=(a+a',x+x',L(a+a') \xrightarrow{i+i'} x+x') \]
where again the natural isomorphism $L(a)+L(a') \cong L(a+a')$ is implicit. The monoidal unit is ${(0_\A,0_\X,{L(0_\A) \to 0_\X})}$.  It is clear that $\Psi \maps (L/\X, \otimes) \maps (\A,+)$ is a strict monoidal functor.   {\john Is the tensor product on $L/\X$ also just $+$?  If so, let's say that and call it $+$.}

The functor $\Psi$ is both a fibration and an opfibration. Suppose we are given a morphism $f \maps a \to b$ in $\A$.  For any object $(b,L(b) \xrightarrow{i} x) \in L/\X$ over $b$, a cartesian lifting of $f$ is given by
\[ (f,1_x) \maps (a,L(a) \xrightarrow{i L(f)} x) \; \to \; (b,L(b) \xrightarrow{i} x) . \]
For any object $(a,L(a) \xrightarrow{i} x)$ in $L/\X$ over $a$, a cocartesian lifting of $f$ is given by
\[ (f,\kappa) \maps (a,L(a) \xrightarrow{i} x) \to (b,L(b) \xrightarrow{\theta} x+_{L(a)} L(b)) \]
where $\kappa$ and $\theta$ arise from the pushout in this diagram:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(a)$};
\node (B) at (2.25,0) {$L(c)$};
\node (C) at (1.5,1) {$L(b)$};
\node (D) at (0,-2) {$x$};
\node (E) at (2.25,-2) {$y$};
\node (F) at (1.5,-1) {$x+_{L(a)} L(b)$};
\path[->,font=\scriptsize,>=angle 90]
(D) edge [dashed] node [above] {$\kappa$} (F)
(F) edge [dashed] node [left] {$\exists ! \psi$} (E)
(D) edge node [above] {$g'$} (E)
(A) edge node [left] {$I$} (D)
(C) edge [dashed] node [left,near end] {$\theta$} (F)
(B) edge node {$$} (E)
(A) edge node[above]{$L(f')$} (B)
(C) edge node [right] {$L(p)$} (B)
(A) edge node[left]{$L(f)$} (C);
\end{tikzpicture}
\]
This diagram also gives the proof that $(f,\kappa)$ is a cocartesian lifting of $f$.
Both cartesian and cocartesian liftings are clearly preserved by the tensor product of $L/\X$, so
$\Psi$ is a monoidal bifibration.

Lastly, we show that $\Psi \maps L/\X \to \A$ satisfies the Beck--Chevalley condition. 
For this, given a pushout square in $\A$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$b$};
\node (C) at (0,-1) {$c$};
\node (D) at (1,-1) {$d$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$h$} (B)
(A) edge node[left]{$k$} (C)
(B) edge node[right]{$g$} (D)
(C) edge node[above]{$f$} (D);
\end{tikzpicture}
\]
we need to show that the natural transformation 
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$(L/\X)_a$};
\node (B) at (1.5,0) {$(L/\X)_b$};
\node (C) at (0,-1) {$(L/\X)_c$};
\node (D) at (1.5,-1) {$(L/\X)_d$};
\node (E) at (0.75,-0.5) {$\Searrow \theta$};
\path[->,font=\scriptsize,>=angle 90]
(B) edge node[above]{$h^*$} (A)
(A) edge node[left]{$k_!$} (C)
(B) edge node[right]{$g_!$} (D)
(D) edge node[below]{$f^*$} (C);
\end{tikzpicture}
\]
defined in Equation \eqref{theta} is an isomorphism.  Let $(b,L(b) \xrightarrow{i} x)$ be an object of $(L/\X)_b$.  Going left, we precompose with $L(h) \maps L(a) \to L(b)$ to obtain the object $(a,L(a) \xrightarrow{i  L(h)} x)$ in $(L/\X)_a$.  Then going down, we push forward along $L(k) \maps L(a) \to L(c)$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(a)$};
\node (B) at (1.5,0) {$x$};
\node (C) at (0,-1) {$L(c)$};
\node (D) at (1.5,-1) {$L(c)+_{L(a)}x$};
\node at (1.1,-0.7) {\Large{$\ulcorner$}};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$I \circ L(h)$} (B)
(A) edge node[left]{$L(k)$} (C)
(B) edge node[right]{$$} (D)
(C) edge node[above]{$\psi$} (D);
\end{tikzpicture}
\]
to obtain the object $(c,L(c) \xrightarrow{\psi} L(c)+_{L(a)} x)$ of $(L/ \X)_c$. For the other route, first going down, we push the object $(b,x,L(b) \xrightarrow{I} x)$ forward along $L(g) \maps L(b) \to L(d)$ by taking the following pushout:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(b)$};
\node (B) at (1.5,0) {$x$};
\node (C) at (0,-1) {$L(d)$};
\node (D) at (1.5,-1) {$L(d)+_{L(b)}x$};
\node at (1.1,-0.7) {\Large{$\ulcorner$}};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$I$} (B)
(A) edge node[left]{$L(g)$} (C)
(B) edge node[right]{$$} (D)
(C) edge node[above]{$\phi$} (D);
\end{tikzpicture}
\]
which yields the object $(d,L(d) \xrightarrow{\theta} L(d)+_{L(b)} x)$ of $(L/\X)_d$.  Then going left, we precompose with $L(f) \maps L(c) \to L(d)$ to obtain the object $(c,L(c) \xrightarrow{\phi L(f)} L(d)+_{L(b)} x)$ of $(L/\X)_c$.

To establish a natural isomorphism between the two objects $(c,L(c)+_{L(a)} x,L(c) \xrightarrow{\psi} L(c)+_{L(a)} x)$ and $(c,L(d)+_{L(b)} x,L(c) \xrightarrow{\theta \circ L(f)} L(d)+_{L(b)} x)$ in $(L/\X)_c$, it suffices to establish a natural isomorphism between the objects $L(c)+_{L(a)} x$ and $L(d)+_{L(b)} x$ in $\X$. The first pushout square above exhibits $L(c)+_{L(a)}x$ as a colimit of the span $$L(c) \xleftarrow{L(k)} L(a) \xrightarrow{I \circ L(h)} x$$in $\X$. On the other hand, as $L$ preserves finite colimits, $L$ preserves pushout squares, and so the following square is also a pushout:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(a)$};
\node (B) at (1,0) {$L(b)$};
\node (C) at (0,-1) {$L(c)$};
\node (D) at (1,-1) {$L(d)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$L(h)$} (B)
(A) edge node[left]{$L(k)$} (C)
(B) edge node[right]{$L(g)$} (D)
(C) edge node[above]{$L(f)$} (D);
\end{tikzpicture}
\]
which we may then paste to the left of the second above pushout square to obtain another pushout square:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(b)$};
\node (B) at (2,0) {$x$};
\node (C) at (0,-1) {$L(d)$};
\node (D) at (2,-1) {$L(d)+_{L(b)}x$};
\node (E) at (-1,0) {$L(a)$};
\node (F) at (-1,-1) {$L(c)$};
\path[->,font=\scriptsize,>=angle 90]
(E) edge node [left] {$L(k)$} (F)
(E) edge node [above] {$L(h)$} (A)
(F) edge node [above] {$L(f)$} (C)
(A) edge node[above]{$I$} (B)
(A) edge node[left]{$L(g)$} (C)
(B) edge node[right]{$$} (D)
(C) edge node[above]{$\theta$} (D);
\end{tikzpicture}
\]
which exhibits $L(d)+_{L(b)} x$ also as a colimit of the same span in $\X$, and hence the desired natural isomorphism between our two objects of $(L /\X)_c$. Thus $\Psi$ satisfies the Beck--Chevalley condition.
\end{proof}
